Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-08 ms.tex
Modify Section 2
From 7450235:
============

In ms.tex,

(*) Modify Section 2
(*) Minor rearrangement of citations in the Introduction

The primary challenge to detection of cosmological H~{\sc i} from the EoR arises from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker. But the inherent differences in spatial isotropy and spectral smoothness can be exploited to extract the cosmological signal from foreground contamination \citep[see, e.g.,][]{dim02,dim04,zal04,fur04,mor04,san05,fur06,mcq06,mor06,wan06,gle08,ali08,ber09,ber10,gho12}. Thus, a detailed characterization of foreground emission has become essential \citep{bow09,liu09,dat10,liu11,mor12,par12b,tro12,pob13,dil13,dil14,liu14a,liu14b,thy13,thy15}.

@@

In wide-field measurements, the steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits. This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths. Typically, an antenna is most sensitive towards its primary field of view relative to the rest of the sky, which in conjunction with the aforementioned wide-field effects results in a characteristic {\it pitchfork} signature in the delay spectrum.

Detailed modeling presented in \citet{thy15} has shown this feature to be a leading source of contamination of the Fourier modes most sensitive to the EoR H~{\sc i} signal. And a dish-shaped antenna is found to yield the most desirable response from a foreground contamination viewpoint. Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot used in their study, the high level of thermal noise prevented a robust confirmation. In this paper, we confirm the {\it pitchfork} signature using deeper data from the MWA.

>>>>

The primary challenge to detection of cosmological H~{\sc i} from the EoR arises from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker. But the inherent differences in spatial isotropy and spectral smoothness can be exploited to extract the cosmological signal from foreground contamination \citep[see, e.g.,][]{dim02,dim04,zal04,fur04,mor04,san05,fur06,mcq06,mor06,wan06,gle08}. Thus, a detailed characterization of foreground emission has become essential \citep{ali08,bow09,liu09,ber09,ber10,dat10,liu11,gho12,mor12,par12b,tro12,pob13,dil13,dil14,liu14a,liu14b,thy13,thy15}.

@@

The defining characteristics of the {\it pitchfork} signature are understood as follows. The steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits in wide-field measurements. This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.

Detailed modeling presented in our original study \citep{thy15} has indicated important implications for future instrument design and analysis algorithms:
\begin{enumerate}
\item positioned adjacent to the Fourier modes most sensitive to the cosmological signal, the {\it pitchfork} feature is a leading source of contamination in these modes, and 
\item of the cases considered, a dish-shaped antenna was found to yield the most desirable response from a foreground contamination viewpoint due to a relatively efficient suppression of sensitivity towards the horizon. 
\end{enumerate}

In this paper, we confirm this key feature using deeper data from the MWA.

% In wide-field measurements, the steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits. This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths. Typically, an antenna is most sensitive towards its primary field of view relative to the rest of the sky, which in conjunction with the aforementioned wide-field effects results in a characteristic {\it pitchfork} signature in the delay spectrum.

% Detailed modeling presented in \citet{thy15} has shown this feature to be a leading source of contamination of the Fourier modes most sensitive to the EoR H~{\sc i} signal. And a dish-shaped antenna is found to yield the most desirable response from a foreground contamination viewpoint. Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot used in their study, the high level of thermal noise prevented a robust confirmation. In this paper, we confirm the {\it pitchfork} signature using deeper data from the MWA.
